\documentclass[20pt]{article}
\usepackage{graphicx}
\setlength\parindent{0pt}
\usepackage{amsfonts}
\usepackage{courier}
\begin{document}
\title{Soundcool's ScModule Specification}
\maketitle

This is a specification for the \texttt{ScModule} superclass that implements methods common to all soundcool modules.
\section*{Attributes}
\subsubsection*{\texttt{context:window.AudioContext}}
instance of Web Audio context to be imported from \texttt{sc-context.js}.
\subsubsection*{\texttt{inputs:Array}}
\texttt{JS Array} containing all inputs to that soundcool module.  
\subsubsection*{\texttt{outputs:Array}}
\texttt{JS Array} containing all outputs to that soundcool module.


\section*{Methods}
\subsubsection*{\texttt{connectTo(destination, sourceOutIndex, destInIndex)}}
\begin{itemize}
\item \texttt{destination}: an instance of a class that inherits \texttt{ScModule}. Specifies which module object to connect to.
\item \texttt{sourceOutIndex}: integer index of the source's \texttt{outputs} attribute. (default: 0)
\item \texttt{destInIndex}: integer index of the \texttt{destination}'s \texttt{inputs} attribute. (default: 0)
\end{itemize}
This method is used to connect two instantiated soundcool objects.

\subsubsection*{\texttt{disconnect(destination, sourceOutIndex, destInIndex)}}
\begin{itemize}
\item \texttt{destination}: an instance of a class that inherits \texttt{ScModule}. Specifies which module object to disconnect.
\item \texttt{sourceOutIndex}: integer index of the source's \texttt{outputs} attribute. (default: 0)
\item \texttt{destInIndex}: integer index of the \texttt{destination}'s \texttt{inputs} attribute. (default: 0)
\end{itemize}
This method is used to disconnect two already connected soundcool objects.

\end{document}